Simulation Study: Unimodal Settings (25% non-null)

### 2018-09-12 datasets/simulations/supplementary/simulations-uasettings-nonnull25.Rmd
Add/modify descriptions of UA setting Rmds; add UA sims w more non-null

---
title: "Simulation Study: Unimodal Settings"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "uasettings-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-benchmark-bimodal.rds")

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_cubic(0.90)              # numeric: proportion of null hypotheses
ts_dist <- rnorm_perturber(1)       # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)      # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

>>>>

---
title: "Simulation Study: Unimodal Settings (25% non-null)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

The simulation settings considered in this study are identical to those carried
out in `simulations-uasettings.Rmd`, with the exception that the proportion of null
hypotheses (pi0) is decreased from 90% to 75%. Here, we investigate the behavior of
FDR-controlling methods under the unimodal setting when the proportion of non-null
hypotheses is substantially larger (25%).

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-25-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "uasettings-25-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-25-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-25-benchmark-bimodal.rds")

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_cubic(0.75)              # numeric: proportion of null hypotheses
ts_dist <- rnorm_perturber(1)       # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)      # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```
